ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-14 pyked.tex
added (very) basic structure
First commit of my part

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ussci}

%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

%====================================================================
\section{Introduction}
%

\section{Conclusions}
%
\blindtext

\blindtext

\section{Acknowledgements}
This research was funded by \ldots

\printbibliography[heading=bibintoc]

>>>>

% !TEX option = -shell-escape
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This work is licensed under the Creative Commons Attribution 4.0
% International License. To view a copy of this license, visit
% http://creativecommons.org/licenses/by/4.0/.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{ussci}

\usepackage{todonotes}
\newcommand\ck{ChemKED}
\usepackage{enumitem}
\setlist{noitemsep}
%======================================================================
\addbibresource{pyked.bib}
%======================================================================
\newcommand\papertopic{Reaction Kinetics}
%======================================================================

@@

%====================================================================
\section{Introduction}
%
\todo[inline]{Kyle to do}

%====================================================================
\section{Related work}
%
\todo[inline]{Kyle to do}

%====================================================================
\section{Overview of format}\label{sec:overview-of-format}

The \ck{} file is a YAML-format file. This format offers the advantage of being
human readable and having parsers in most common programming languages,
including Python, C++, Java, Perl, MATLAB, and many others. The YAML syntax is
quite simple. The basic file structure is made of mappings, delimited by a colon:

\begin{minted}{yaml}
    key: value
    key: 10 # This is because YAML syntax highlighting in Atom is busted
\end{minted}

In addition, sequences can be specified by using a hypen \yaml|-| or square
brackets

\begin{minted}{yaml}
    - [0, 1, 2]
    key:
      - 0
      - 1
      - 2
\end{minted}

The \ck{} format is designed
to include all of the information necessary to simulate a given experiment. Most
of the required information is specified as a \yaml|key| with a \yaml|value|.

In
general, this includes

\todo{Make this smaller}
\begin{itemize}
    \item The type of experiment
    \begin{itemize}
        \item Ignition delay
        \item Flame speed
        \item Speciation
        \item Extinction
    \end{itemize}
    \item The experimental apparatus
    \begin{itemize}
        \item Shock tube
        \item Rapid compression machine
        \item Counterflow flame
        \item Burner-stabilized flame
    \end{itemize}
    \item The thermodynamic conditions of the experiment
    \begin{itemize}
        \item Temperature
        \item Pressure
        \item Composition
    \end{itemize}
    \item Apparatus specific effects
    \begin{itemize}
        \item Non-ideal pressure rise in shock tubes
        \item Post-compression heat loss in rapid compression machines
    \end{itemize}
\end{itemize}

%====================================================================
\section{Use example}
%
\todo[inline]{Bryan/Kyle to do}

%====================================================================
\section{Conclusions and future work}
%
\todo[inline]{both to do}

%====================================================================
\section{Acknowledgements}
This research was funded by \ldots
\todo[inline]{update}

\printbibliography
